On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-09-27 paper.tex
Written down definition of eq. rel

\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\UU}{\hat{\mathrm{U}}}      % Unipotent subgroup on the Steinberg level
\newcommand{\StB}{\hat{\mathrm{B}}}     % Borel subgroup on the Steinberg level
\newcommand{\StH}{\hat{\mathrm{H}}}     % Torus on the Steinberg level
\newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
\newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations

@@

By definition, $\Sym(\Phi, R)$ is the subgroup of $\St(\Phi, R)$ generated by all Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
 If $\rk(\Phi)\geq 2$ it is clear that $\Sym(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ contained in $\K_2(\Phi, R)$.

@@

\begin{equation}
 \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r] & \St(\Phi, R/I) \ar[r] & 1 }
\end{equation}

@@

\subsection{Factorization theorem} 
Throughout this section $A$ denote a commutative local ring with the maximal ideal $M$.

Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.

%Similarly $\Sym(\Phi, A[t, t^{-1}], M[t, t^{-1}]$ denotes the subgroup of $\St(\Phi, A[t, t^{-1}], M[t, t^{-1}])$ generated by elements of the form $h_\alpha(1+q)^{}$
As before $A$ is a commutative local ring with the maximal ideal $M$.

@@

Denote by $V_0$ the set $\St(\Phi, A[t]) \times H(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], M[t, t^{-1}])$. 
We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 3 elementary transformations:
\begin{enumerate}
 \item $(a \cdot j_+^*(p), b, \beta) \sim (a, H(p) \cdot b, \beta)$, where $p$ is an element $\UU(\Phi^+,A[t])$;
 \item $(a \gamma, b, \beta) \sim (a, b, ?(\gamma)^b \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], M[t])$;
\end{enumerate}

>>>>

\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\UU}{\hat{\mathrm{U}}}      % Unipotent subgroup on the Steinberg level
\newcommand{\StB}{\hat{\mathrm{B}}}     % Borel subgroup on the Steinberg level
\newcommand{\StH}{\hat{\mathrm{H}}}     % Torus on the Steinberg level
\newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
\newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
\newcommand{\ext}[1]{\mu_{#1}}           % Map from St(Ф, R, I) --> St(Ф, R)

@@

By definition, $\Sym(\Phi, R)$ is the subgroup of $\St(\Phi, R)$ generated by all Steinberg symbols $\{a, b\}_\alpha$, $a, b \in R^*$. 
$\Sym(\Phi, R)$ is contained in $\K_2(\Phi, R)$ and is a central subgroup of $\St(\Phi, R)$ provided $\rk(\Phi)\geq 2$.

@@

\begin{equation}
 \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r]^{\ext{R}} & \St(\Phi, R) \ar[r]^{\pi_*} & \St(\Phi, R/I) \ar[r] & 1 }
\end{equation}

\begin{multline}
 \{ t, u \}'_\alpha = h_{\alpha}(u) ^ {h_{?}(t)} =  y_\alpha(t(u-1)) \cdot y_{-\alpha}\left(-t^{-1}(u^{-1}-1)\right)^{x_\alpha(-t)} \cdot y_\alpha\left(t(u-1)\right)^{w_\alpha(-t)} \cdot \\
\cdot y_\alpha(u-1) \cdot y_{-\alpha}\left(-(u^{-1}-1)\right)^{x_\alpha(-1)} \cdot y_\alpha(u-1)^{w_\alpha(-1)}.
\end{multline}

@@

\subsection{Factorization theorem} 
Throughout this section $A$ denote a commutative local ring with the maximal ideal $m$.
Denote by $H(R) \subseteq \St(\Phi, R)$ the composite of the two subgroups $\Sym(\Phi, R)$ and $\UU(\Phi^+, R)$.

@@

Denote by $V_0$ the set $\St(\Phi, A[t]) \times \StH(A[t, t^{-1}]) \times \St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$. 
We define an equivalence relation $\sim$ on $V_0$ as the minimal equivalence relation generated by the following 3 elementary transformations:
\begin{enumerate}
 \item $(a \cdot u, b, \beta) \sim (a, j_+^*(u) \cdot b, \beta)$, where $u$ is an element $\UU(\Phi^+, A[t])$;
 \item $(a \cdot \ext{A[t]}(\gamma), b, \beta) \sim (a, b, j^*_+(\gamma)^b \cdot \beta)$, where $\gamma$ is an element of $\St(\Phi, A[t], m[t])$;
  %and $b$ acts on $j^*_+(\gamma)$ via the conjugation action of $\St(\Phi, R)$ on $\St(\Phi, A[t, t^{-1}], m[t, t^{-1}])$;
 \item $(a, b \cdot u, \beta) \sim (a, b, u\cdot \beta)$, where $u$ is an element of $\UU(\Phi^+, m[t, t^{-1}])$;
 \item $(a, b \cdot \{ t, a \}_\alpha, \beta) \sim (a, b, \{ t, a \}'_\alpha \cdot \beta) $, where $a \in (1+m)^*$
  and $\{t, a\}'_\alpha$ is a relative Steinberg symbol discussed in ???
\end{enumerate}
